---
title: "rand"
author: "Bram"
date: "14 September 2017"
output: html_document
---

armies
```{r}
n=20
```

rownames first (warning: growing vector)
```{r}
for(i in 1:n){
  if (i<3){
    first<<-c(1,2,1,2)
  } else {
    tmp=c(rep.int(i,times=i-1),1:i)
    first<<-c(first,tmp)
  }
}
rm(list=c("i","tmp"))
```

rownames second (warning: growing vector)
```{r}
for(i in 1:n){
  if (i<3){
    second<<-c(1,1,2,2)
  } else {
    tmp=c(1:i,rep.int(i,times=i-1))
    second<<-c(second,tmp)
  }
}
rm(list=c("i","tmp"))
```

old rownames
first=c(1,2,1,2,3,3,1:4,4,4,1:5,rep.int(5,3),1:6,rep.int(6,4),1:7,rep.int(7,5),1:8,rep.int(8,6),1:9,rep.int(9,7),1:10,rep.int(10,8),1:11,rep.int(11,9),1:12,rep.int(12,10),1:13,rep.int(13,11),1:14,rep.int(14,12),1:15,rep.int(15,13),1:16,rep.int(16,14),1:17,rep.int(17,15),1:18,rep.int(18,16),1:19,rep.int(19,17),1:20,rep.int(20,18),1:20)
second=c(1,1,2,2,1,2,3,3,3,1:4,rep.int(4,3),1:5,rep.int(5,4),1:6,rep.int(6,5),1:7,rep.int(7,6),1:8,rep.int(8,7),1:9,rep.int(9,8),1:10,rep.int(10,9),1:11,rep.int(11,10),1:12,rep.int(12,11),1:13,rep.int(13,12),1:14,rep.int(14,13),1:15,rep.int(15,14),1:16,rep.int(16,15),1:17,rep.int(17,16),1:18,rep.int(18,17),1:19,rep.int(19,18),1:20,rep.int(20,19))

rownames
```{r}
rown=numeric(n*n)
for(i in 1:length(rown)){
  rown[i]=paste(as.character(first[i]),"v",as.character(second[i]))
}
rm(list=c("i"))
rown
```

matrix
```{r}
mat=matrix(numeric(n*n*(n+1)),nrow=n*n)
rownames(mat)=rown
colnames(mat)=0:n
```

outcomes
```{r}
onvon=c(21/36,15/36)
tovon=c(91/216,125/216)
trvon=c(441/1296,855/1296)
tovto=c(275*0.75/972,14*0.25/54,660*0.75/972,40*0.25/54,37*0.75/972)
trvto=c(1763*0.5/3888,162*0.5/648,1337*0.5/3888,486*0.5/648,788*0.5/3888)
```

create first four rows
```{r}
mat[1,1]=onvon[2]
mat[1,2]=onvon[1]
mat[2,1]=tovon[2]
mat[2,2]=onvon[2]*tovon[1]
mat[2,3]=onvon[1]*tovon[1]
mat[3,1]=onvon[2]*onvon[2]
mat[3,2]=onvon[1]+(onvon[1]*onvon[2])
mat[4,1]=tovto[5]+(tovto[4]*mat[2,1])
mat[4,2]=(tovto[2]*mat[3,1])+(onvon[2]*tovto[3])+(tovto[4]*mat[2,2])
mat[4,3]=tovto[1]+(tovto[2]*mat[3,2])+(tovto[3]*onvon[1])+(tovto[4]*mat[2,3])
```


create mv1
```{r}
for(i in (4*(n+1)+1):length(mat)){
  x=rown[floor((i-1)/(n+1))+1]
  m=first[floor((i-1)/(n+1))+1]
  e=second[floor((i-1)/(n+1))+1]
  l=ifelse(i%%(n+1)==0,20,(i%%(n+1))-1)
  if(l>m){
    mat[x,as.character(l)]=0
  } else if(e==1&l==0){
      mat[x,as.character(l)]=trvon[2]
    } else if(e==1){
        mat[x,as.character(l)]=mat[paste((m-1),"v",1),as.character(l-1)]*trvon[1]
      } else{
        mat[x,as.character(l)]=mat[x,as.character(l)]
        }
}
rm(list=c("e","i","l","m","x"))
```

create 1vm
```{r}
for(i in (4*(n+1)+1):length(mat)){
  x=rown[floor((i-1)/(n+1))+1]
  m=first[floor((i-1)/(n+1))+1]
  e=second[floor((i-1)/(n+1))+1]
  l=ifelse(i%%(n+1)==0,20,(i%%(n+1))-1)
  if(l>m){
    mat[x,as.character(l)]=0
  } else if(m==1&l==0){
      mat[x,as.character(l)]=mat[paste(1,"v",(e-1)),1]*onvon[2]
  } else if(m==1){
      mat[x,as.character(l)]=(mat[paste(1,"v",(e-1)),2]*onvon[2])+onvon[1]    
  } else {
      mat[x,as.character(l)]=mat[x,as.character(l)]    
        }
}
rm(list=c("e","i","l","m","x"))
```

create 2vm
```{r}
for(i in (4*(n+1)+1):length(mat)){
  x=rown[floor((i-1)/(n+1))+1]
  m=first[floor((i-1)/(n+1))+1]
  e=second[floor((i-1)/(n+1))+1]
  l=ifelse(i%%(n+1)==0,20,(i%%(n+1))-1)
  if(l>m){
    mat[x,as.character(l)]=0
  } else if(m==2&l==0){
      mat[x,as.character(l)]=(mat[paste(2,"v",e-1),1]*tovto[4])+(mat[paste(2,"v",e-2),1]*tovto[5])
  } else if (m==2&l==1){
      mat[x,as.character(l)]=(mat[paste(1,"v",e),1]*tovto[2])+(mat[paste(1,"v",e-1),1]*tovto[3])+(mat[paste(2,"v",e-1),2]*tovto[4])+(mat[paste(2,"v",e-2),2]*tovto[5])    
  } else if (m==2&l==2){
      mat[x,as.character(l)]=tovto[1]+(mat[paste(1,"v",e),2]*tovto[2])+(mat[paste(1,"v",e-1),2]*tovto[3])+(mat[paste(2,"v",e-1),3]*tovto[4])+(mat[paste(2,"v",e-2),3]*tovto[5])    
  } else {
      mat[x,as.character(l)]=mat[x,as.character(l)]
        }
}
rm(list=c("e","i","l","m","x"))
```

create mv2
```{r}
for(i in (4*(n+1)+1):length(mat)){
  x=rown[floor((i-1)/(n+1))+1]
  m=first[floor((i-1)/(n+1))+1]
  e=second[floor((i-1)/(n+1))+1]
  l=ifelse(i%%(n+1)==0,20,(i%%(n+1))-1)
  if(l>m){
    mat[x,as.character(l)]=0
  } else if(e==2&l==0){
      mat[x,as.character(l)]=trvto[5]+(mat[paste(m,"v",1),1]*trvto[4])
  } else if (e==2&l==1){
      mat[x,as.character(l)]=(mat[paste((m-1),"v",2),1]*trvto[2])+(mat[paste((m-1),"v",1),1]*trvto[3])+(mat[paste(m,"v",1),2]*trvto[4])    
  } else if (e==2&l>1){
      mat[x,as.character(l)]=(mat[paste((m-2),"v",2),l-1]*trvto[1])+(mat[paste((m-1),"v",2),l]*trvto[2])+(mat[paste((m-1),"v",(e-1)),l]*trvto[3])+(mat[paste(m,"v",1),l+1]*trvto[4])    
  } else {
      mat[x,as.character(l)]=mat[x,as.character(l)]    
        }
}
rm(list=c("e","i","l","m","x"))
```

create the rest
```{r}
for(i in (4*(n+1)+1):length(mat)){
  x=rown[floor((i-1)/(n+1))+1]
  m=first[floor((i-1)/(n+1))+1]
  e=second[floor((i-1)/(n+1))+1]
  l=ifelse(i%%(n+1)==0,20,(i%%(n+1))-1)
  if(l>m){
    mat[x,as.character(l)]=0
  } else if(m>2&e>2&l==0){
      mat[x,as.character(l)]=(mat[paste(m,"v",(e-1)),1]*trvto[4])+(mat[paste(m,"v",(e-2)),1]*trvto[5])
  } else if (m>2&e>2&l==1){
      mat[x,as.character(l)]=(mat[paste((m-1),"v",e),1]*trvto[2])+(mat[paste((m-1),"v",(e-1)),1]*trvto[3])+(mat[paste(m,"v",(e-1)),2]*trvto[4])+(mat[paste(m,"v",(e-2)),2]*trvto[5])    
  } else if (m>2&e>2&l>1){
      mat[x,as.character(l)]=(mat[paste((m-2),"v",e),l-1]*trvto[1])+(mat[paste((m-1),"v",e),l]*trvto[2])+(mat[paste((m-1),"v",(e-1)),l]*trvto[3])+(mat[paste(m,"v",(e-1)),l+1]*trvto[4])+(mat[paste(m,"v",(e-2)),l+1]*trvto[5])    
  } else {
      mat[x,as.character(l)]=mat[x,as.character(l)]    
        }
}
rm(list=c("e","i","l","m","x"))
```

save (optional, remove the hashtag)
#```{r}
#install.packages("xlsx")
library(xlsx)
getwd()
filename=paste(getwd(),"/Risk Dice (",as.character(n),"v",as.character(n),").xlsx",sep="")
write.xlsx(mat,filename)
```

